HO unification from object language to meta language

### 2024-03-23 paper/appendix.tex
unmess renaming

  type decompl-subst map -> map -> ho.subst -> 
    fo.subst -> fo.subst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (fv VO) (hv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->fm Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (hv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

@@

  type add-new-map-aux ho.subst -> list ho.tm -> map -> 
        map ->  fo.subst -> fo.subst -> o.
  add-new-map-aux _ [] _ [] S S.
  add-new-map-aux H [T|Ts] L L2 S S2 :- 
    add-new-map H T L L1 S S1, 
    add-new-map-aux H Ts L1 L2 S1 S2.

  type add-new-map ho.subst -> ho.tm -> map -> 
      map ->  fo.subst -> fo.subst -> o.
  add-new-map _ (ho.uva N _) Map [] F1 F1 :- 
    mem Map (mapping _ (hv N _)), !.
  add-new-map H (ho.uva N L) Map [Map1 | MapL] F1 F3 :-
    mem.new F1 M F2,
    len L Arity, Map1 = mapping (fv M) (hv N (arity Arity)),
    add-new-map H (ho.app L) [Map1 | Map] MapL F2 F3.
  add-new-map H (ho.lam B) Map NewMap F1 F2 :- 
    pi x\ add-new-map H (B x) Map NewMap F1 F2.
  add-new-map H (ho.app L) Map NewMap F1 F3 :- 
    add-new-map-aux H L Map NewMap F1 F3.
  add-new-map _ (ho.con _) _ [] F F :- !.
  add-new-map _ N _ [] F F :- name N.

  type complete-mapping-under-ass ho.subst -> ho.assignment -> 
    map -> map ->  fo.subst -> fo.subst -> o.
  complete-mapping-under-ass H (ho.val Val) Map1 Map2 F1 F2 :- 
    add-new-map H Val Map1 Map2 F1 F2.
  complete-mapping-under-ass H (ho.abs Abs) Map1 Map2 F1 F2 :- 
    pi x\ complete-mapping-under-ass H (Abs x) Map1 Map2 F1 F2.

  type complete-mapping ho.subst -> ho.subst ->   
    map -> map -> fo.subst -> fo.subst -> o.
  complete-mapping _ [] L L F F.
  complete-mapping H [none | Tl] L1 L2 F1 F2 :-   
    complete-mapping H Tl L1 L2 F1 F2.
  complete-mapping H [some T0 | Tl] L1 L3 F1 F3 :-
    ho.deref-assmt H T0 T,
    complete-mapping-under-ass H T L1 L2 F1 F2, 
    append L1 L2 LAll,
    complete-mapping H Tl LAll L3 F2 F3.

  type decompile map -> links -> ho.subst -> 
    fo.subst -> fo.subst -> o.
  decompile Map1 L HO FO FO2 :- 
    commit-links L L1_ HO HO1, !,
    complete-mapping HO1 HO1 Map1 Map2 FO FO1,
    decompl-subst Map2 Map2 HO1 FO1 FO2.
\end{elpicode}

>>>>

  type decompl-subst map -> map -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (fv VO) (hv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->fm Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (hv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

@@

  type add-new-map-aux ho.subst -> list ho.tm -> map -> 
        map ->  fo.fsubst -> fo.fsubst -> o.
  add-new-map-aux _ [] _ [] S S.
  add-new-map-aux H [T|Ts] L L2 S S2 :- 
    add-new-map H T L L1 S S1, 
    add-new-map-aux H Ts L1 L2 S1 S2.

  type add-new-map ho.subst -> ho.tm -> map -> 
      map ->  fo.fsubst -> fo.fsubst -> o.
  add-new-map _ (ho.uva N _) Map [] F1 F1 :- 
    mem Map (mapping _ (hv N _)), !.
  add-new-map H (ho.uva N L) Map [Map1 | MapL] F1 F3 :-
    mem.new F1 M F2,
    len L Arity, Map1 = mapping (fv M) (hv N (arity Arity)),
    add-new-map H (ho.app L) [Map1 | Map] MapL F2 F3.
  add-new-map H (ho.lam B) Map NewMap F1 F2 :- 
    pi x\ add-new-map H (B x) Map NewMap F1 F2.
  add-new-map H (ho.app L) Map NewMap F1 F3 :- 
    add-new-map-aux H L Map NewMap F1 F3.
  add-new-map _ (ho.con _) _ [] F F :- !.
  add-new-map _ N _ [] F F :- name N.

  type complete-mapping-under-ass ho.subst -> ho.assignment -> 
    map -> map ->  fo.fsubst -> fo.fsubst -> o.
  complete-mapping-under-ass H (ho.val Val) Map1 Map2 F1 F2 :- 
    add-new-map H Val Map1 Map2 F1 F2.
  complete-mapping-under-ass H (ho.abs Abs) Map1 Map2 F1 F2 :- 
    pi x\ complete-mapping-under-ass H (Abs x) Map1 Map2 F1 F2.

  type complete-mapping ho.subst -> ho.subst ->   
    map -> map -> fo.fsubst -> fo.fsubst -> o.
  complete-mapping _ [] L L F F.
  complete-mapping H [none | Tl] L1 L2 F1 F2 :-   
    complete-mapping H Tl L1 L2 F1 F2.
  complete-mapping H [some T0 | Tl] L1 L3 F1 F3 :-
    ho.deref-assmt H T0 T,
    complete-mapping-under-ass H T L1 L2 F1 F2, 
    append L1 L2 LAll,
    complete-mapping H Tl LAll L3 F2 F3.

  type decompile map -> links -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompile Map1 L HO FO FO2 :- 
    commit-links L L1_ HO HO1, !,
    complete-mapping HO1 HO1 Map1 Map2 FO FO1,
    decompl-subst Map2 Map2 HO1 FO1 FO2.
\end{elpicode}
